Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-18 final_metrics_analysis.Rmd

>>>>

```{python EDA}
X_new_index = X_new.rename(columns={"race": "def_race"})
X_new_index = X_new_index.rename(columns={"sex": "def_sex"})
# renaming dataframe columns to avoid the ValueError of variables being a column AND index label (which is ambiguous)

X_new_index.groupby(["def_race"])["age"].median()
X_new_index.groupby(["def_race", "sex"]).size()
X_new_index.groupby(["def_race", "c_charge_degree"]).size()
X_new_index.groupby(["def_race"])["priors_count"].median()
#X_new_index.groupby(["def_race"])["juv_fel_count"].median()
#X_new_index.groupby(["def_race"])["juv_misd_count"].median()
# above two lines commented out since medians for everyone = 0

```
